Characterizing Stellar Streams by ML

### 2023-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

    Per \autoref{eq:stream_and_bkg_prob} the stream is a conditionally independent
    addition of both astrometric and photometric models.
    In astrometrics the stream is a Gaussian track in $\phi_2$ and
    parallax $\varpi$, using the model defined in
    \autoref{ssub:method:astrometric_model:on_stream}. We use a 4-layer 
    (\texttt{LinTanh} with shape (1 input, 64 hidden, 4 output), where the 4 outputs
    are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
    The network is small, but sufficiently large to permit 15\% dropout and retain
    robust predictions.
    The photometric model is a distance modulus-shifted isochrone, using the model
    outlined in  \autoref{ssub:method:photometric_model:on_stream}. We use the
    same isochrone parameters as were used to simulate the stream. For this mock
    stream we demonstrate simultaneous astrometric and photometric modeling, linking
    the distance modulus and parallax track, as explained in
    \autoref{ssub:method:linking_to_astrometrics}. Thus the photometric model
    does not have its own network, using instead the outputs
    $[\mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
    The background model is split in two components, the first is a uniform distribution
    in $\phi_2$, the second an exponential.

>>>>

    Per \autoref{eq:stream_and_bkg_prob} the stream is a conditionally independent
    addition of both astrometric and photometric models.
    In astrometrics the stream is a Gaussian track in $\phi_2$ and
    parallax $\varpi$, using the model defined in
    \autoref{ssub:method:astrometric_model:on_stream}. We use a 4-layer 
    (\texttt{LinTanh} with shape (1 input, 64 hidden, 4 output), where the 4 outputs
    are $[\mu_{\phi_2}, \sigma_{\phi_2}, \mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
    The network is small, but sufficiently large to permit 15\% dropout and retain
    robust predictions.
    The photometric model is a distance modulus-shifted isochrone, using the model
    outlined in  \autoref{ssub:method:photometric_model:on_stream}. We use the
    same isochrone parameters as were used to simulate the stream. For this mock
    stream we demonstrate simultaneous astrometric and photometric modeling, linking
    the distance modulus and parallax track, as explained in
    \autoref{ssub:method:linking_to_astrometrics}. Thus the photometric model
    does not have its own network, using instead the outputs
    $[\mu_{\varpi}, \sigma_{\varpi}](\phi_1)$.
    The background model is split in two components, the first is a uniform distribution
    in $\phi_2$, the second is an exponential distribution for $\varpi$.
    The uniform distribution does not have any parameters, and thus no neural network.
    The exponential distribution has only the slope parameter and we use a 3-layer 
    (\texttt{LinTanh} with shape (1, 32, 1) and 15\% dropout.
